Enforced Invariant Confluence

### 2018-04-26 doc/paper/sections/evaluation.tex
Shrunk some of the TPC-C description.

  % \item
    Two of the twelve invariants involve generating \textbf{sequential and
    unique identifiers}. Consider, for example, invariant 2 which dictates that
    a district's next order id \ttt{D\_NEXT\_O\_ID} is equal to the maximum
    order id \ttt{O\_ID} of orders within the district. The New Order
    transaction places an order with \ttt{O\_ID} equal to the current value of
    \ttt{D\_NEXT\_O\_ID} and then increments \ttt{D\_NEXT\_O\_ID}. We model
    this workload with three objects. \ttt{D\_NEXT\_O\_ID} is modeled as an
    integer merged by $\max$. The order table is modelled as two objects. The
    first is a set of all order ids used, merged by union. The second is a map
    which maps order id to order. The map's merge function performs an id-by-id
    merge of orders. If two different orders have the same id, the merge
    function replaces them with a distinguished value to indicate that the
    primary key constraint has been violated. We applied Lucy to this workload
    and in less than a second, it produced a counterexample that---when
    labelled as reachable---proved that the workload was not
    \invariantconfluent{}.
% \end{enumerate}

>>>>

  % \item
    Two of the twelve invariants involve generating \textbf{sequential and
    unique identifiers}. Consider, for example, invariant 2 which dictates that
    a district's next order id \ttt{D\_NEXT\_O\_ID} is equal to the maximum
    order id \ttt{O\_ID} of orders within the district. The New Order
    transaction places an order with \ttt{O\_ID} equal to the current value of
    \ttt{D\_NEXT\_O\_ID} and then increments \ttt{D\_NEXT\_O\_ID}.
    We model this workload with an integer for \ttt{D\_NEXT\_O\_ID} and a map
    for \ttt{O\_ID} that maps order ids to order.
    %
    % We model this workload with three objects. \ttt{D\_NEXT\_O\_ID} is modeled
    % as an integer merged by $\max$. The order table is modelled as two objects.
    % The first is a set of all order ids used, merged by union. The second is a
    % map which maps order id to order. The map's merge function performs an
    % id-by-id merge of orders. If two different orders have the same id, the
    % merge function replaces them with a distinguished value to indicate that
    % the primary key constraint has been violated.
    %
    We applied Lucy to this workload and in less than a second, it produced a
    counterexample that---when labelled as reachable---confirming that the
    workload is \emph{not} \invariantconfluent{}~\cite{bailis2014coordination}.
% \end{enumerate}
